Trajectory model of passive kelp dispersal

### 2020-06-29 thesis_chapter_3.Rmd
updates to outputs and rmd files for chapters 1,2 and 3. Updated figures to follow and final chpater 2 to follow

The the velocity of the kelp sporophyte is a function of mass and time, as the mass of the individual will vary temporarily with changes in growth rate, fragmentation and epibiont load (mass), which in turn will effect buoyancy and thereby the surface area exposed to wind drag and seawater drag. A momentum equation can be used to describe how the mass of the kelp individual changes temporarily. A previous study by @Andersson2017 who used this approach to describe the change in velocity of an iceberg over time which has been adapted to suite the current project; and taking into account the additional parameterisitions:
$$m\frac{du_i}{dt} = F_{corr} + F_{a} + F_{c} + F_{r} + F_{e}$$
where $m$ is the overall kelp mass, $V_{i}$ is the initial kelp velocity, $d$ is the distance, $F_{corr}$ is Coriolis Force, $F_{a}$ is the air drag force, $F_c$ is the seawater drag force, $F_r$ is the effect of waves on the kelp, $F_{e}$ is the epibiont load force.

>>>>

The the velocity of the kelp sporophyte is a function of mass and time, as the mass of the individual will vary temporarily with changes in growth rate, erosion and epibiont load (mass), which in turn will effect buoyancy and thereby the surface area exposed to wind drag and seawater drag.

A momentum equation can be used to describe how the mass of the kelp individual changes temporarily. A previous study by @Andersson2017 who used this approach to describe the change in velocity of an iceberg over time which has been adapted to suite the current project; and taking into account the additional parameterisitions:
$$m\frac{du_i}{dt} = F_{corr} + F_{a} + F_{c} + F_{r} + F_{e}$$
where $m$ is the overall kelp mass, $u_{i}$ is the starting kelp velocity, $d$ is the distance, $F_{corr}$ is Coriolis Force, $F_{a}$ is the air drag force, $F_c$ is the seawater drag force, $F_r$ is the effect of waves on the kelp, $F_{e}$ is the epibiont load force.
